Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-10 ms.qmd
Updated with bubble plots needs some adjustments

options(digits = 3, scipen = 3)
```

@@

Daniel W.A. Noble$^1$, Fonti Kar$^2$, Frank Seebacher$^3$, Alex Bush$^4$, & Shinichi Nakagawa$^2$

@@

```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))

@@

p8.1.2 <- p8.1 / p8.2

ggsave(p8.1.2, filename = "./output/figures/fig8.png")
```

```{r, fig9, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))

@@

p91.2 <- p9.1 / p9.2

ggsave(p91.2, filename = "./output/figures/fig9.png")
```

@@

p67 <- (p6 | p7) + plot_annotation(tag_levels = "A")

ggsave(p67, filename = "./output/figures/fig6.png", height = 10, width = 30, units = "cm")
```

@@

p89 <- (p8 | p9) + plot_annotation(tag_levels = "A")

ggsave(p89, filename = "./output/figures/fig7.png", height = 10, width = 30, units = "cm")
```

>>>>

  options(digits = 2, scipen = 3)
```

@@

<p style="text-align: center;">Daniel W.A. Noble$^1$, Fonti Kar$^2$, Frank Seebacher$^3$, Alex Bush$^4$, & Shinichi Nakagawa$^2$</p>

@@

```{r}
#| label: fig-fig8
#| fig-align: center
#| fig-cap: Bubble plot environment lnRR for wild populations by habitat
 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))

@@

p8.1.2 <- p8.1 / p8.2
p8.1.2
ggsave(p8.1.2, filename = "./output/figures/fig8.png")
```

```{r}
#| label: fig-fig9
#| fig-align: center
#| fig-cap: Bubble plot environment lnRR for wild populations by habitat
 col <- c("#0871B9", "#F3B40D", "#1BB908")
p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))

@@

p91.2 <- p9.1 / p9.2
p91.2
ggsave(p91.2, filename = "./output/figures/fig9.png")
```

@@

p67 <- (p6 | p7) + plot_annotation(tag_levels = "A")
p67
ggsave(p67, filename = "./output/figures/fig6.png", height = 10, width = 30, units = "cm")
```

@@

p89 <- (p8 | p9) + plot_annotation(tag_levels = "A")
p89
ggsave(p89, filename = "./output/figures/fig7.png", height = 10, width = 30, units = "cm")
```
